---
# This is a yaml header.  It includes document metadata.
title: "Project: Modeling with Classification Trees"
# Fill in author below and change output to word_document if you prefer 
# to compile to word. These hashtagged lines will be ignored by R when 
# compiling the document.
author: "Ali Ladha"
output: html_document  
---

```{r setup, include=FALSE}
# This is a code chunk.  It starts and ends with three backticks. It includes 
# a header defined by curly braces.  Minimally the header requires an "r" to tell 
# RMarkdown that this will be an R code chunk. include = F means that this code chunk 
# will not be printed when the document is knitted.

knitr::opts_chunk$set(echo = TRUE) 
# This code sets global options for the document. echo = TRUE means that when 
# the document is compiled the code from each chunk will be displayed along with 
# the results.

library(tidyverse)
# This code loads the tidyverse package.

library(rpart)
library(rpart.plot)
# This code loads the other packages needed for this assignment.

# Run the entire code chunk by clicking the green arrow in the upper right of the chunk.  Alternatively
# run execute individual lines by positioning the cursor anywhere on the line 
# and hitting control-return. The results will be displayed below the code chunk.

```

## Introduction

Data analysis should be reproducible, meaning: every step taken to manipulate, clean, transform, summarize, visualize or model data should be documented exactly so that results can be replicated.  RMarkdown is a tool---or, specifically, a document type---for doing reproducible data science by keeping the code for a project together with the written  analysis and interpretation.   

This is an RMarkdown template that you can use for calculating answers to the project quiz questions for this module. You will also knit this document to HTML (or Word) and submit it for the File Upload assignment.

RMarkdown uses a very simple markup language.  For example, rather than interacting with a menu to format the text, as in MS Word, you use simple code outside of the code chunks:

- A dash and a space at the beginning of a line (as here) creates a bullet point for use in a list.
- A number with a period at the beginning of a line creates a numbered list.
- Hashtags create headings (#), subheadings (##) or sub-subheadings (###).
- Emphasis can be added with asterisks like this: *italics* and **bolding.**

## Notes on compiling this document  

- Change the information in the yaml header above:  title and author.
- Make sure the output argument is set correctly.  It should read: output: html_document or output: word_document.
- Once you are finished writing the code necessary to answer the questions in the quiz, clear your environment by clicking on the broom icon in the environment pane (upper right quadrant).
- Run each code chunk individually (click the green arrow icon in the upper right of the chunk). Start at the top of this document and proceed sequentially to the bottom.  Fix any code errors you find.  
- Once your code is error-free, click "knit" in the menu above. Your document should compile to HTML, if the output is set to "html_document" (or to word if the output is set to "word_document").

In the code chunk above (entitled "setup") echo is set to TRUE.  This means that the code in your chunks will be displayed, along with the results, in your compiled document.

## Load and Transform Data

Below is code to clean and prepare the dataset for modeling. Before running that code, follow these preparatory steps:

1. After downloading the RMarkdown template and the dataset for the assignment from Canvas, make sure to  copy or move these files from your downloads folder to a folder dedicated to this class--say, MKTG-6487.
2. You need to define that folder as your "working directory."  To do so, navigate to that folder using the files tab in the lower right quadrant in RStudio.  (You should see your files you moved into this folder in the previous step.) Click the "More" button in the menu under the Files tab and select "Set As Working Directory."

Once the files are in the right location on your computer then run this code to clean and format the data:

```{r}
# You must run this code to format the dataset properly!

advise_invest <- read_csv("adviseinvest.csv")  |>            # Download data and save it (via assignment operator)
  select(-product) |>                                        # Remove the product column
  filter(income > 0,                                          # Filter out mistaken data
         num_accts < 5) |> 
  mutate(answered = ifelse(answered==0, "no","yes"),          # Turn answered into yes/no 
         answered = factor(answered,                          # Turn answered into factor
                           levels  = c("no", "yes")),         # Specify factor levels
         female = factor(female),                             # Make other binary and categorical                                                                                                        # variables into factors
         job = factor(job),
         rent = factor(rent),
         own_res = factor(own_res),
         new_car = factor(new_car),
         mobile = factor(mobile),
         chk_acct = factor(chk_acct),
         sav_acct = factor(sav_acct)) 

```

## Questions

Use the code chunks below to write code that will enable you to answer the questions in the project quiz.

Some of the questions do not require writing code and have been omitted from this template.

### Q2.

```{r}
mean(advise_invest$answered == "yes")
# OR ifelse(advise_invest$answered == "yes", 1,0) %>% mean()
# OR advise_invest %>% count(answered)
  #16124/29499
```

### Q3.  


```{r}
income_model <- rpart(formula = answered ~ income, data = advise_invest)
income_model

rpart.plot(income_model)

(predict(income_model, type = "class") == advise_invest$answered) %>% mean()
  #OR you can use rpart and manually calculate it by taking observations and subtracting them by lossing and dividing that
  # by total sum of observations:
  # (8063-2944) + (1152-256) + (1792 - 640) + (17212-6592) + 256 + (1024-128) / 29499
```

### Q4. 


```{r}
```
The classification tree algorithm automatically splits data to maximize information gain (while minimizing entropy). This ensures a good result as the data is split more homogeneously. The focus of the algorithm is to have a higher information gain, and have a lower entropy. An Entrophy of 0 would mean that the leaf nodes would all be either answered or unanswered. Whereas an Entropy of 1 means they are equally split.


### Q5. 


```{r}
tree_model <- rpart(formula = answered ~., data = advise_invest, maxdepth = 4)
tree_model

rpart.plot(x = tree_model, tweak = 1.2, roundint = T)
```

Based on the plot the most important predictions is the: Chk_acct, income, and mobile variables.

### Q6.


```{r}
(predict(income_model, type = "class") ==  (advise_invest$answered)) %>% mean()

(predict(tree_model, type = "class") == (advise_invest$answered)) %>% mean()
```
The tree_model is better since it has a higher accuracy rate.